 

### 2023-04-24 thesis_final_version.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

bibliography: main.bib
# natbiboptions: "numbers"
csl: https://www.zotero.org/styles/the-lancet

  # intro: intro.bib
  # ch1: chapter1.bib
  #

acronyms:
  insert_loa: false
  loa_title: ""

  # loa_title: "List of Acronyms"
  keys:
    - shortname: LMIC
      longname: low and middle income country

---

@@

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. To capture premature mortality due to mental disorders, as well as disability from associated causes, we proposed a composite approach to estimation. Using the most recently available estimates from the Global Burden of Disease study, we found that the burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. The economic value of this mental health burden was estimated to exceed 4.7 trillion USD using a value of statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.

@@

In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic. Using an interrupted time series approach with search data from U.S. counties, states, and international trends, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression. These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

@@

@@

# Acronyms with acronym down
# Separate bibliography for each section
# Numbered figures and tables by section

# Check that sequential articles are represented by a dash
# Table of figures and tables
# Institutional authors need to be fixed in bibliography

>>>>

bibliography: main.bib
csl: https://www.zotero.org/styles/the-lancet
acronyms:
  insert_loa: false
  insert_links: false
  loa_title: ''
  keys:
    - shortname: DALYs
      longname: disability-adjusted life years
    - shortname: YLLs
      longname: years of life lost 
    - shortname: YLDs
      longname: years of healthy life lost due to disability 
    - shortname: LMICs
      longname: low- and middle-incomee countries
    - shortname: WHO
      longname: World Health Organization
    - shortname: USD
      longname: United States dollars
    - shortname: GBD
      longname: Global Burden of Disease
    - shortname: GBO
      longname: Global Health Observatory
    - shortname: GDP
      longname: gross domestic product
    - shortname: NCDs
      longname: noncommunicable diseases
    - shortname: PAF
      longname: population attributable fraction
    - shortname: VSL
      longname: value of a statistical life
    - shortname: IRB
      longname: Institutional Review Board 
    - shortname: UIs
      longname: uncertainty intervals
    - shortname: CIs
      longname: confidence intervals
    - shortname: PPP
      longname: purchasing power parity
    - shortname: CCEs
      longname: climate change-related exposures
    - shortname: HMIS
      longname: health management information system
    - shortname: ESA CCI
      longname: European Space Agency’s Climate Change Initiative
    - shortname: ESA CCI SM
      longname: ESA CCI soil moisture dataset
    - shortname: ERA5
      longname: 'European ReAnalysis 5' 
    - shortname: NOAA
      longname: United States National Oceanic and Atmospheric Administration
    - shortname: GESIS
      longname: Gestion du Système d'Information Sanitaire
    - shortname: DHIS2
      longname: 'District Health Information Software 2'
    - shortname: CSB
      longname: centre santé de base
    - shortname: FSB
      longname: formation sanitaires privées de dase
    - shortname: CHD/CHRD
      longname: centre hospitalier de référence de district
    - shortname: RHINO
      longname: Routine Health Information Network
    - shortname: USAID
      longname: United States Agency for International Development
    - shortname: US
      longname: United States
    - shortname: CHRR
      longname: centre hospitalier de référence régionale
    - shortname: CHU
      longname: centre hospitalier universitaire
    - shortname: C3S
      longname: Copernicus Climate Change Service
    - shortname: ECMWF
      longname: European Centre for Medium-Range Weather Forecasts
    - shortname: km
      longname: kilometers
    - shortname: MFR La Réunion
      longname: Météo-France La Réunion
    - shortname: WMO
      longname: World Meteorological Organisation
    - shortname: RSMC 
      longname: Regional Specialized Meteorological Center
    - shortname: NB
      longname: negative binomial
    - shortname: IRRs
      longname: incidence rate ratios
    - shortname: FE
      longname: fixed effects
    - shortname: CDC
      longname: Centers for Disease Control and Prevention
    - shortname: FDA
      longname: Food and Drug Administration
    - shortname: EUA
      longname: Emergency Use Authorization
    - shortname: MIT
      longname: Massachusetts Institute of Technology
    - shortname: FIPS
      longname: Federal Information Processing Standards
    - shortname: USDA
      longname: United States Department of Agriculture
    - shortname: ITS
      longname: interrupted time series
    - shortname: CITS
      longname: controlled interrupted time series
    - shortname: MDD
      longname: major depressive disorder
    - shortname: ADHD
      longname: attention deficit hyperactivity disorder
    - shortname: CoC
      longname: clouding of consciousness
    - shortname: GAD
      longname: generalized anxiety disorder
---

@@

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. To capture premature mortality due to mental disorders, as well as disability from associated causes, we proposed a composite approach to estimation. Using the most recently available estimates from the Global Burden of Disease study, we found that the burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. The economic value of this mental health burden was estimated to exceed 4.7 trillion United States dollars using a value of statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.

@@

In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic. Using an interrupted time series approach with search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression. These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

@@

\section*{List of Acronyms}

\addcontentsline{toc}{section}{List of Acronyms}

\printacronyms

@@

# Check that sequential articles are represented by a dash
# Institutional authors need to be fixed in bibliography
# Numbered figures and tables by section
